\vspace*{5ex}
\begin{center}
\framebox{\bf \large ACADEMIC PUBLIC LICENSE FOR THE USE OF STEPSS}
\end{center}

{\bf \large 1. Definitions related to the software}

``Software'' means a copy of STEPSS, which is distributed under this Academic Public License. ``Work based on the Software'' means either the Software or any derivative work under copyright law: that is to say, a work containing the Software or a portion of it, either verbatim or with modifications. ``Using the Software'' means any act of creating executables that contain or directly use libraries that are part of the Software, running any of the tools that are part of the Software, or creating works based on the Software. ``You'' refers to each licensee.

{\bf \large 2. Authors}

STEPSS has been developed by Dr Petros Aristidou (email: petros.aristidou@cut.ac.cy) and\\
Dr Thierry Van Cutsem (email: thierry.h.van.cutsem@gmail.com), hereafter referred to as the ``Authors''.

{\bf \large 3. Intellectual property rights}

STEPSS is made up of three modules: PFC (for power flow computations), RAMSES (the solver of differential-algebraic equations), and CODEGEN (a tool to develop models).

PFC and CODEGEN are the property of Dr.\ Thierry Van Cutsem. RAMSES is the property of the University of Li\`ege, Belgium, which has granted to both Authors a personal, royalty-free, limited, non-exclusive, non-transferable and non-assignable license to distribute free of charge an executable version of RAMSES in accordance with the terms detailed under Articles 4, 5 and 6 below.

{\bf \large 4. License terms}

Permission is hereby granted to use the Software free of charge for any non-commercial purpose, including teaching and research at universities, colleges and other educational institutions, research at non-profit research institutions, and personal non-profit purposes. For using the Software for commercial purposes, including but not restricted to consulting activities, design of commercial hardware or software products, or if you are a commercial entity participating in research projects, you have to contact the Authors.

You are not required to accept this License. Nothing else grants you permission to use the Software; the law prohibits this action if you do not accept this License. Therefore, by using the Software (or any work based on the Software), you indicate your acceptance of this License and all its terms and conditions.

{\bf \large 5. Warranty}

The Software is provided ``as is'', without warranty of any kind, express or implied, including but not limited to the warranties of merchantability, fitness for a particular purpose and non-infringement. In no event shall the Authors nor the Intellectual property owners be liable for any claim, damages or other liability, whether in an action of contract, tort or otherwise, arising from, out of or in connection with the software or the use or other dealings in the Software.

{\bf \large 6. Limited version of the Software}

This free-of-charge version of the software is limited to power system models up to 1000 buses (or nodes) and can be executed with parallelization using no more than two cores. For extensions to larger models or execution using more than two cores, you have to contact the Authors.
