\section{\index{PLOTSTEP@PLOT\_STEP}Sampling time for observed variables}

\$PLOT\_STEP time(s) ;

\section{\index{DISPPROF@DISP\_PROF}Display Profiling Results}

\$DISP\_PROF T/F ; 

\section{\index{GPREFRESHRATE@GP\_REFRESH\_RATE}Run-time observables refresh
	interval}

\$GP\_REFRESH\_RATE time\_interval(s) ;


\section{\index{OBSBUFFERSIZE@OBS\_BUFFER\_SIZE}Observable buffer size}

\$OBS\_BUFFER\_SIZE size(GB) ;

Internal memory reserved for storing observables during simulation.
Default: 8~GB. Set this to less than half of the available RAM for
large simulations.


\section{\index{SPARSESOLVER@SPARSE\_SOLVER}Sparse solver}

\$SPARSE\_SOLVER KLU/ma41 ;

Selects the sparse linear solver used for Jacobian factorization.
Default: KLU.


\section{\index{TLOADREST@T\_LOAD\_REST}Time constant of load restoration}

 \$T\_LOAD\_REST time(s) ; 


\section{\index{OMEGAREF@OMEGA\_REF}Omega Reference}

 \$OMEGA\_REF SYN/COI ; 

Synchronous reference frame or center of inertia reference frame.


\section{\index{MAXFAULT@MAX\_FAULT}Maximum Fault Value}

 \$MAX\_FAULT value ; 


\section{\index{SBASE@S\_BASE}Base Power}

Sets the global base power of the system.

 \$S\_BASE BASE(MVA) ; 


\section{\index{FNOM}Nominal Frequency}

 FNOM Frequency(Hz) ; 


\section{\index{NEWTONTOLER@NEWTON\_TOLER}Newton Tolerance}

 \$NEWTON\_TOLER NETWORK\_TOLERANCE INJ\_RELATIVE\_TOLERANCE
	INJ\_ABSOLUTE\_TOLERANCE ; 

Set's the solver Newton iteration tolerance for stopping. Default
values are: 1e-03, 5e-04, 5e-04.


\section{\index{FINDIFFER@FIN\_DIFFER}Finite Difference Values}

 \$FIN\_DIFFER proportional\_value absolute\_value
	; 

Values used to calculate numerically Jacobian matrices of injectors.


\section{\index{FULLUPDATE@FULL\_UPDATE}Full Jacobian Update}

 \$FULL\_UPDATE T/F ; 

Disable partial Jacobian updates.


\section{\index{SKIPCONV@SKIP\_CONV}Skip Converged Blocks}

\$SKIP\_CONV T/F ; 

Activate/Deactivate stopping to solve converged injectors.


\section{\index{LATENCY}Latency Tolerance}

 \$LATENCY OBS\_TIME\_WINDOW(s) EARLY\_STOP(T/F)
	; 


\section{\index{SCHEME}Solution Scheme}

 \$SCHEME DE/IN ; 

Integrated or Decomposed solution scheme.


\section{\index{NB_THREADS@NB\_THREADS}Number of Threads for parallel computing}

 \$NB\_THREADS Number ;


\section{\index{NB_CHUNKS@NB\_CHUNKS}Way of injector distribution over parallel
	threads}

 \$OMP STA/DYN/GUI chunk ;

STA is for static assignment (better for NUMA architecture computers),
DYN is for dynamic assignment (better for UMA architecture computers)
and GUI is for guided. Chunk is the number of consecutive injectors
assigned to each thread.


\section{Update network elements with frequency}

 \$NET\_FREQ\_UPD T/F ;

Check \href{file:models/freq_upd_vminmax.pdf}{Network update with frequency}.


\section{\index{CALLGP@CALL\_GP}Call Gnuplot}

 \$CALL\_GP T/F ;

If set to F, the observables are still written to file but Gnuplot is not
launched. Use this for batch processing and for runs on machines without a
display. Default: T.


\section{\index{GPMODE@GP\_MODE}Gnuplot output mode}

 \$GP\_MODE term/png ;

With {\tt term} the curves are shown in an interactive Gnuplot terminal; with
{\tt png} they are written to PNG files instead. Default: {\tt term}.


\section{\index{ZMIN}Minimum branch impedance}

 \$ZMIN value(pu) ;

Lower bound imposed on the magnitude of a branch impedance. Branches with a
smaller impedance are clamped to this value, which prevents the network
admittance matrix from becoming singular. Default: $10^{-5}$~pu.


\section{\index{LATSUBNETS@LAT\_SUBNETS}Latency on subnetworks}

 \$LAT\_SUBNETS T/F ;

Applies the latency treatment at the level of the subnetworks, in addition to
the injectors. Default: F.


\section{\index{BASEMDL@BASE\_MDL}Load a compiled model library}

 \$BASE\_MDL filename ;

Loads a compiled user-model library (MDL) at start-up, so that user-defined
models can be used without relinking the executable.

\faHandPointRight~This record is only acted upon by the Windows build made with
the Intel compiler. On the other platforms it is accepted and silently ignored;
there, user-defined models must be linked in with URAMSES instead.


\section{\index{LICENSE}License key}

 \$LICENSE email license\_key ;

Unlocks the full version, removing the limits of the free version stated at the
beginning of this document (1000 buses and 2~cores). The key is 64~characters
long and is tied to the electronic mail address given in the same record. Both
are provided by the authors; contact them as indicated in Section~\ref{ch-overview}.
Without this record the free-version limits apply.